method-qc

### 2017-09-18 analysis/method-qc.Rmd
added kinds of output

```{r}
library(googlesheets)
library(cowplot)
rules_info <- gs_title("Trajectory Inference Methods") %>% gs_read(skip=1)
```

```{r}
ggplot(rules_info,aes(log(Citations+1),`QC score`))+
  geom_smooth(method='lm',formula=y~x) +
  geom_point() +
  ggrepel::geom_label_repel(aes(label=Name))

ggplot(rules_info,aes(log(Citations+1),`QC score`))+
  geom_smooth(method='lm',formula=y~x) +
  geom_point() +
  ggrepel::geom_label_repel(aes(label=Name))

@@

ggplot(rules_info,aes(date,`QC score`))+
  geom_smooth(method='lm',formula=y~x) +
  geom_point() +
  ggrepel::geom_label_repel(aes(label=Name))

@@

ggplot(rules_info,aes(published,`QC score`))+
  geom_violin() +
  geom_point() +
  ggrepel::geom_text_repel(aes(label=Name))

@@

>>>>

```{r}
library(googlesheets)
library(cowplot)
library(tidyverse)
rules_info <- gs_title("Trajectory Inference Methods") %>% gs_read(skip=1)
```

```{r}
ggplot(rules_info,aes(log(Citations+1), qc_score))+
  geom_smooth(method='lm',formula=y~x) +
  geom_point() +
  ggrepel::geom_label_repel(aes(label=name))

ggplot(rules_info,aes(log(Citations+1), qc_score))+
  geom_smooth(method='lm',formula=y~x) +
  geom_point() +
  ggrepel::geom_label_repel(aes(label=name))

@@

ggplot(rules_info,aes(date, qc_score))+
  geom_smooth(method='lm',formula=y~x) +
  geom_point() +
  ggrepel::geom_label_repel(aes(label=name))

@@

ggplot(rules_info,aes(published, qc_score))+
  geom_violin() +
  geom_point() +
  ggrepel::geom_text_repel(aes(label=name))

@@

Different methods generate different kinds of output...
```{r}
rules_info %>% filter(wrapper == "Done") %>% select(ids, output) %>% 
  separate_rows(ids, sep=",") %>% 
  separate_rows(output, sep=",") %>% 
  mutate(output=trimws(output)) %>% 
  ggplot() + 
    geom_bar(aes(output)) +
    coord_flip()
```
